### 2017-07-07 Manuscript/Annexes/ssc.tex
Correct file heading and add italic to simulation period.
Correct reference to point to top of image. Correct spacing for figure using \centering in place of center environment. Correct math in chapter 3 and add note to Morris.
Add power from EnergyPlus and Modelica. Correct error in figure and add list of models used.

\begin{figure}
    \begin{center}
            \includegraphics[page=4]{Ressources/Images/Modelisation/circulateur.pdf}
    \end{center}
    \caption{Fiche technique du circulateur \textit{Wilo-YonosECO 25/1-5 BMS}.
             \label{fig:caracs_pompes}}
\end{figure}

\begin{figure}
    \begin{center}
            \includegraphics[page=1]{Ressources/Images/Modelisation/Radco_308C_HP_plan.pdf}
    \end{center}
    \caption{Certification $ICC-SRCC$ pour le capteur \textit{Radco 308C HP}.
             \label{fig:caracs_radco}}
\end{figure}

\begin{figure}
    \begin{center}
            \includegraphics[page=1]{Ressources/Images/Modelisation/SkyPro_12_CPC58_tube.pdf}
    \end{center}
    \caption{Certification $ICC-SRC$C pour le capteur \textit{Sky Pro 12 CPC58}.
             \label{fig:caracs_skypro}}
\end{figure}

>>>>

%!TEX root = ../main.tex
% Annexes/ssc.tex

\begin{figure}
    \centering
    \includegraphics[page=4]{Ressources/Images/Modelisation/circulateur.pdf}
    \caption{Fiche technique du circulateur \textit{Wilo-YonosECO 25/1-5 BMS}.
             \label{fig:caracs_pompes}}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[page=1]{Ressources/Images/Modelisation/Radco_308C_HP_plan.pdf}
%     \caption{Certification $ICC-SRCC$ pour le capteur \textit{Radco 308C HP}.
%              \label{fig:caracs_radco}}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/SkyPro/din_skyPro.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Kloben Sky Pro 12 CPC58}.
             \label{fig:caracs_skypro}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/IDMK/din_idmk.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Sonnenkraft IDMK-25AL}.
             \label{fig:caracs_idmk}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/Eco/din_eco.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Dima Energy + Eco}.
             \label{fig:caracs_eco}}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{Ressources/Images/Modelisation/Capteurs/CPCStar/din_CPCStar.pdf}
    \caption{Certification \textit{Solar Keymark} pour le capteur \textit{Ritter CPC $14$ Star}.
             \label{fig:caracs_star}}
\end{figure}

### 2017-07-07 Manuscript/Chapitres/Chap1-ContexteTravaux.tex
Add power from EnergyPlus and Modelica. Correct error in figure and add list of models used.

\begin{align}\label{eq:iam_dir_tube_lon}
    K_{\theta l,\,dir} (\theta) = 1 &- b_{0} \times \left(\frac{1}{\cos(\theta)} - 1\right)
                          - b_{1} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{2} \\
                          &- b_{2} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{3}
                          - b_{3} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{4} \\
\end{align}

>>>>

\begin{align}\label{eq:iam_dir_tube_lon}
    K_{\theta l,\,dir} (\theta) = 1 &+ b_{0} \times \left(\frac{1}{\cos(\theta)} - 1\right)
                          + b_{1} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{2} \\
                          &+ b_{2} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{3}
                          + b_{3} \times \left(\frac{1}{\cos(\theta)} - 1\right)^{4} \\
\end{align}
